---
title: "gsize trials"
output: html_document
---

```{r}
library(ggplot2)
setwd("~/projects/gsize/")
```

Start with RIMMAs because Paul's script can't handle hapmap2 paired end reads. Mapped RIMMAs to v3 version 22 of the cDNA with only "known" cDNAs, then counted abundance only of genes with proportion read mapping < 5E-5

Get data
```{r}
#genome size
rimma_gs<-read.csv("~/projects/gsize/data/gsize_rimma.csv",header=T)
#percent mapping, change columns, fix filenames
rimma_perc<-read.csv("~/projects/gsize/results/fixed_genes_percent.txt",header=F)
colnames(rimma_perc)=c("Line","total_reads","tota_genes","mapped_reads","mapped_genes","percent")
rimma_perc$Line=gsub(".fastq.bam.txt","",gsub("abundance.","",rimma_perc$Line))
rimma_data<-merge(rimma_gs,rimma_perc,by="Line")
```

Correlation and plot.
```{r}
ggplot(data=rimma_data,aes(x=gsize,y=percent))+geom_point()+geom_smooth(method="lm")+xlab("1C genome size")+ylab("Fraction Reads Aligning to corrected cDNA")
cor.test(rimma_data$gsize,rimma_data$percent)
```

Solid negative correlation, but not fantastic $r^2$.  The genome sizes for these lines come from a *different individual* from the same accession, so we don't expect great correlation.

Get some data on relative genome size from HapMap2 and those reads mapped to Ensembl v3 version 22 of the cDNA with only "known" cDNAs
```{r}
#Genome size from Chia
g=pipe(paste("curl -o - https://gist.githubusercontent.com/rossibarra/7638160/raw/62c4dab3f8a96a7d86cfe01a524dc1df2d03784f/genome_size"))
gsize<-read.table(g,header=T,colClasses=c("character","numeric","numeric"))

#Mapping to v3 cDNA ("known" cdna only)
#m=pipe(paste("ssh farm 'cat ~/projects/genomesize/results/percent_hm2.txt'"))

#percent mapping, change columns, fix filenames
hm2_perc<-read.csv("~/projects/gsize/results/fixed_genes_percent.txt",header=F)
colnames(hm2_perc)=c("Line","total_reads","tota_genes","mapped_reads","mapped_genes","percent")
hm2_perc$Line=gsub("_merged.fq.bam.txt","",gsub("abundance.","",hm2_perc$Line))

#Munge away: get lines with both genome size and percent mapping
data<-merge(gsize,hm2_perc,by="Line")
```

Test correlation
```{r}
ggplot(data=data,aes(x=GenomeSize,y=percent))+geom_point()+geom_smooth(method="lm")+xlab("1C genome size")+ylab("Fraction Reads Aligning to cDNA")
cor.test(data$GenomeSize,data$percent)
```

Significant is good, but positive correlation is not what we predict. Let's remove TILs and see what happens
```{r}
x=data[c(1:24,34:35),]
ggplot(data=x,aes(x=GenomeSize,y=percent))+geom_point()+geom_smooth(method="lm")+xlab("1C genome size")+ylab("Fraction Reads Aligning to cDNA")
cor.test(x$GenomeSize,x$percent)
```

Still sucky.  Will need to go back and revisit filtering. For now, ugh.
